---
title: "Credible Regions on RS Optima"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.height = 3,
  fig.width = 6,
  out.extra = 'style = "border-color:white"'
)
```

## 1. Credible Regions on Linear Models

```{r include=FALSE}
library(tidyverse)
library(mvtnorm)
library(lhs)
library(nloptr)
library(parallel)
library(microbenchmark)
library(grDevices)
library(keras)
library(geometry)
library(rjags)
library(fields)
library(gridExtra)
library(MASS)
```

```{r}
# only for development
n_rep <- 5
sd_noise <- 2
n_post <- 200
constr_lb <- rep(-sqrt(2), 2)
constr_ub <- rep(sqrt(2), 2)
```

### 1.0 Simulate Experimental Data

#### Quadratic Polynomials in 2 Factors
```{r}
quad_2 <- function(x, beta) {
  beta[1] + beta[2] * x[1] + beta[3] * x[2] +
    beta[4] * x[1]^2 + beta[5] * x[2]^2 + beta[6] * x[1] * x[2]
}
```

```{r}
quad_2_grad <- function(x, beta) {
  rbind(
    beta[2] + 2 * beta[4] * x[1] + beta[6] * x[2],
    beta[3] + 2 * beta[5] * x[2] + beta[6] * x[1]
  )
}
```

#### True Function
```{r}
# only for development 
# beta_true <- matrix(c(72, -11.78, 0.74, -7.25, -7.55, -4.85), nrow = 6)
# optimum_true <- cbind(-0.9285643, 0.3472541)
beta_true <- matrix(c(90.79, -1.095, -1.045, -2.781, -2.524, -0.775), nrow = 6)
optimum_true <- cbind(-0.1716998, -0.1806523)
non_optima <- tibble(
  x1 = c(1.2, 1.5, 0.5, 0.2, 2, rep(1, 5)),
  x2 = c(rep(1, 5), 1.2, 1.5, 0.5, 0.2, 2)
) %>% 
  pmap_df(~ tibble(x1 = ..1 * optimum_true[1], x2 = ..2 * optimum_true[2])) %>%
  as.matrix()
```

```{r eval=FALSE, include=FALSE}
beta2stat_pt <- function(beta) {
  b <- matrix(c(beta[2], beta[3]), nrow = 2)
  B <- matrix(c(
    beta[4], beta[6] / 2,
    beta[6] / 2, beta[5]
  ), nrow = 2)
  -solve(B, b) / 2
}
beta2stat_pt(beta_true)
```

### Experimental Design
```{r}
# only for development
# design <- cbind(
#   x1 = runif(n, constr_lb[1], constr_ub[1]), x2 = runif(n, constr_lb[2], constr_ub[2])
# )
design_no_rep <- cbind(
  x1 = c(-1, 1, -1, 1, -sqrt(2), sqrt(2), rep(0, 5)),
  x2 = c(-1, -1, 1, 1, 0, 0, -sqrt(2), sqrt(2), rep(0, 3))
) %>% 
  rbind(
    cbind(
      x1 = runif(11, constr_lb[1], constr_ub[1]), 
      x2 = runif(11, constr_lb[2], constr_ub[2])
    )
  )
```

```{r}
design <- design_no_rep[rep(1:nrow(design_no_rep), n_rep), ]
```


#### Simulated Observations under IID Noises

```{r}
# only for development 
f <- apply(design, 1, quad_2, beta_true) %>% 
  as.matrix(nrow = nrow(design))
y <- f + rnorm(n = nrow(design) , mean = 0, sd = sd_noise) 
```

### 1.1 Draw Posterior Samples $\{\beta\}$

#### Model
$$
  \mathbf{y} \,|\, \mathbf{\beta}, \sigma^2, \mathbf{X} 
  \sim N(\mathbf{X\beta}, \sigma^2 \mathbf{I})
$$

#### Prior 
$$
p(\mathbf{\beta}, \sigma^2, \,|\, \mathbf{X}) \propto \frac{1}{\sigma^2}
$$

#### Posterior
$$
\mathbf{\beta} \,|\, \mathbf{y}, \mathbf{X} 
\sim t_{n-p} \left(\hat{\mathbf{\beta}}, \, s^2(\mathbf{X}^T\mathbf{X})^{-1}\right)
$$

where 
$$
\hat{\mathbf{\beta}} = (\mathbf{X}^T\mathbf{X})^{-1} \mathbf{X}^T \mathbf{y}
$$
$$
s^2 = \frac{\Vert \mathbf{y} - \mathbf{X}\hat{\mathbf{\beta}} \Vert^2}{n-p}
$$
```{r}
draw_post_quad_2 <- function(design, y, n_post) {
  X <- as.data.frame(design) %>%
    pmap_df(~ tibble(
      intercept = 1, x1 = ..1, x2 = ..2,
      x1x1 = ..1^2, x2x2 = ..2^2, x1x2 = ..1 * ..2
    )) %>%
    as.matrix(nrow = nrow(design)) # assume full quadratic
  beta_hat <- solve(crossprod(X), crossprod(X, y))
  s2 <- crossprod(y - X %*% beta_hat) / (nrow(design) - ncol(X))
  betas_post <- mvtnorm::rmvt(
    n = n_post, sigma = as.numeric(s2) * solve(crossprod(X)), df = nrow(design) - ncol(X),
    delta = beta_hat
  ) %>% t() # use argument delta instead of mu to avoid fallacy
  list(betas_post = betas_post, beta_hat = beta_hat)
}
```

```{r}
# only for development
c(betas_post, beta_hat) %<-% draw_post_quad_2(design = design, y = y, n_post = n_post)
```

### 1.2 Construct the Map $h(\beta)$

$$
  x^* = h(\beta) = \underset{x \in R}{\arg\max} \, f(x; \beta )
$$
```{r}
generate_initial_solutions <- function() {
  lhs::geneticLHS(n = 5, k = 2, criterium = "Maximin") %>%
    sweep(MARGIN = 2, STATS = constr_ub - constr_lb, FUN = "*") %>%
    sweep(MARGIN = 2, STATS = constr_lb, FUN = "+")
}
```

```{r}
x0s <- generate_initial_solutions()
```

```{r eval=FALSE, include=FALSE}
# Optimize the Posterior Mean Model from a Single Initial Solution
res <- nloptr(
  x0 = x0s[5, ],
  eval_f = function(x) -quad_2(x, beta_hat),
  eval_grad_f = function(x) -quad_2_grad(x, beta_hat),
  lb = constr_lb, ub = constr_ub,
  opts = list("algorithm" = "NLOPT_LD_MMA", print_level = 0, xtol_rel = 1e-03)
)
res$solution
```

```{r eval=FALSE, include=FALSE}
# Optimize from Multiple Initial Solutions
nloptr_quad_2 <- purrr::partial(nloptr::nloptr,
  eval_f = function(x) -quad_2(x, beta_hat),
  eval_grad_f = function(x) -quad_2_grad(x, beta_hat),
  lb = constr_lb, ub = constr_ub,
  opts = list("algorithm" = "NLOPT_LD_MMA", print_level = 0, xtol_rel = 1e-03)
)
opt <- lapply(1:nrow(x0s), function(i) x0s[i, ]) %>%
  lapply(function(i) nloptr_quad_2(x0 = i)) %>%
  map_df(~ tibble(
    x1 = .x$solution[1], x2 = .x$solution[2], objective = -.x$objective
  )) %>%
  top_n(1, objective) %>%
  distinct() %>%
  select(c(x1, x2))
opt
```

```{r}
beta2opt <- function(beta, constr_lb, constr_ub, x0s) {
  nloptr_quad_2 <- purrr::partial(nloptr::nloptr,
    eval_f = function(x) -quad_2(x, beta),
    eval_grad_f = function(x) -quad_2_grad(x, beta),
    lb = constr_lb, ub = constr_ub,
    opts = list("algorithm" = "NLOPT_LD_MMA", print_level = 0, xtol_rel = 1e-03)
  )
  lapply(1:nrow(x0s), function(i) x0s[i, ]) %>%
    purrr::map(function(i) nloptr_quad_2(x0 = i)) %>%
    map_df(~ tibble(
      x1 = .x$solution[1], x2 = .x$solution[2], objective = -.x$objective
    )) %>%
    top_n(1, objective) %>%
    distinct() %>%
    dplyr::select(x1, x2) 
}
```

```{r}
# only for development
optimum_mean <- beta2opt(
  beta = beta_hat, constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s
)
```

### 1.3 Compute Posterior Optima $\{h(\beta)\}$

#### Sequential implementation

```{r}
beta2opt_apply <- function(betas_post, constr_lb, constr_ub, x0s) {
  apply(betas_post, 2, beta2opt, constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s) %>%
    map_df(~ tibble(x1 = .x$x1, x2 = .x$x2)) %>%
    as.matrix()
}
```

```{r eval=FALSE, include=FALSE}
# only for development
optima_post <- beta2opt_apply(betas_post = betas_post,
                              constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s)
```

#### Parallel implementation

```{r}
beta2opt_parApply <- function(betas_post, constr_lb, constr_ub, x0s) {
  cl <- makeCluster(detectCores(logical = FALSE) - 1)
  clusterEvalQ(cl, {
    library(tidyverse)
    library(nloptr)
  })
  clusterExport(cl, c("x0s", "quad_2", "quad_2_grad", "constr_lb", "constr_ub"))
  optima_post <- parApply(cl, betas_post, 2, beta2opt,
                          constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s) %>%
    map_df(~ tibble(x1 = .x$x1, x2 = .x$x2)) %>%
    as.matrix()
  stopCluster(cl)
  optima_post
}
```

```{r eval=FALSE, include=FALSE}
# only for development
optima_post <- beta2opt_parApply(betas_post = betas_post,
                                 constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s)
```

```{r eval=FALSE, include=FALSE}
# Benchmark different implementations
microbenchmark(m1 = beta2opt_parApply(), m2 = beta2opt_apply(), times = 1)
```

### 1.4 Main Function

```{r}
BayesOptRegionQuad <- function(design, y, n_post, constr_lb, constr_ub, x0s, parallel = TRUE) {
  # 1. draw posterior betas:
  c(betas_post, beta_hat) %<-% draw_post_quad_2(design = design, y = y, n_post = n_post)
  # 2. construct the map from beta to optimum
  ## initial solutions: see "generate_initial_solutions"
  ## objective function: see "quad_2"
  ## gradient of objective function: see "quad_2_grad"
  ## the map: see "beta2opt"
  # 3. map posterior betas to optima
  if(parallel) {
    optima_post <- beta2opt_parApply(
      betas_post = betas_post, constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s
    )
  } else{
    optima_post <- beta2opt_apply(
      betas_post = betas_post, constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s
    )
  }
  optimum_mean <- beta2opt(
    beta = beta_hat, constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s
  ) 
  # 4. return
  structure(
    list(
      optima_post = optima_post, optimum_mean = optimum_mean,
      constr_lb = constr_lb, constr_ub = constr_ub
    ),
    class = "bayescrquad"
  )
}
```

```{r}
plot.bayescrquad <- function(res) {
  res$optima_post %>%
    as_tibble() %>%
    slice(chull(x1, x2)) %>%
    ggplot(aes(x = x1, y = x2)) +
    geom_polygon(col = "black", fill = "white", alpha = 0) +
    geom_point(data = res$optimum_mean, aes(x = x1, y = x2), col = "red") +
    xlab(expression(x[1])) + ylab(expression(x[2])) +
    xlim(constr_lb[1], constr_ub[1]) + ylim(constr_lb[2], constr_ub[2]) +
    coord_fixed() +
    theme_bw() +
    theme(
      panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
      axis.title.x = element_text(size = 15),
      axis.title.y = element_text(size = 15)
    )
}
```

```{r}
res <- BayesOptRegionQuad(
  design = design, y = y, n_post = n_post, 
  constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s
)
```

<center>
```{r fig.height=5, fig.width=5, out.extra='style="border-color:white"', echo=FALSE}
plot(res)
```
<\center>

```{r eval=FALSE, include=FALSE}
# only for development
BayesOptRegionQuad_benchmark <- purrr::partial(
  BayesOptRegionQuad, design = design, y = y, n_post = n_post,
  constr_lb = constr_lb, constr_ub = constr_ub
)
microbenchmark(
  m1 = BayesOptRegionQuad_benchmark(parallel = TRUE),
  m2 = BayesOptRegionQuad_benchmark(parallel = FALSE),
  times = 1
)
```

### 1.5 Coverage Analyses

```{r include=FALSE}
inCR <- function(new_point, old_points) {
  old_points <- as.matrix(old_points)
  dim(new_point) <- c(1, 2)
  # indices of the points lying the convex hull
  coords <- grDevices::chull(old_points)
  # area of the convex hull
  CR_area <- geometry::polyarea(old_points[coords, 1], old_points[coords, 2])
  # add the new point to the set and re-calculate the area
  r <- rbind(old_points, new_point)
  newCH_coords <- chull(r)
  new_area <- geometry::polyarea(r[newCH_coords, 1], r[newCH_coords, 2])
  # tell if the new point is in the original convex hull by comparing the areas
  if (new_area > CR_area) FALSE else TRUE
}
```
```{r eval=FALSE, include=FALSE}
# test "inCR"
inCR(old_points = res$optima_post, new_point = optimum_true)
```

```{r,eval=FALSE, include=FALSE}
cover_one_time <- function(i, design, f, sd_noise, n_post, constr_lb, constr_ub, x0s,
                           optimum_true, non_optima) {
  print(paste(i, "th CR with", "sd_noise =", sd_noise, "and n_rep =", nrow(design) / 22))
  res <- BayesOptRegionQuad(
    design = design,
    y = f + rnorm(n = nrow(design), mean = 0, sd = sd_noise),  
    n_post = n_post, constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s, parallel = FALSE
  )
  opt_in <- inCR(new_point = optimum_true, old_points = res$optima_post)
  indices <- grDevices::chull(res$optima_post)
  area <- geometry::polyarea(res$optima_post[indices, 1], res$optima_post[indices, 2])
  non_opt_in <- apply(X = non_optima, MARGIN = 1, FUN = inCR, old_points = res$optima_post)
  list(opt_in = opt_in, area = area, non_opt_in = non_opt_in)
}
```
```{r eval=FALSE, include=FALSE}
# only for development
res_cover_one_time <- cover_one_time(
  i = 1, 
  design = design, f = f, sd_noise = sd_noise, 
  n_post = n_post, constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s,
  optimum_true = optimum_true, non_optima = non_optima
)
```

```{r,eval=FALSE, include=FALSE}
cover_multiple_time <- function(sd_noise, n_rep, n_post, n_cov, 
                                design_no_rep, beta_true, constr_lb, constr_ub, x0s,
                                optimum_true, non_optima) {
  design <- design_no_rep[rep(1:nrow(design_no_rep), n_rep), ]
  f <- apply(design, 1, quad_2, beta_true) %>% 
    as.matrix(nrow = nrow(design))
  cl <- makeCluster(detectCores(logical = FALSE) - 1, outfile = "")
  clusterEvalQ(cl, {
    library(tidyverse)
    library(nloptr)
    library(keras)
  })
  clusterExport(
    cl, c(
      "cover_one_time",
      "quad_2", 
      "BayesOptRegionQuad",
      "draw_post_quad_2", "quad_2_grad", "beta2opt", "beta2opt_apply", "beta2opt_parApply",
      "inCR"
    )
  )
  res <- clusterApply(
    cl = cl, x = 1:n_cov, fun = cover_one_time,
    design = design, f = f, sd_noise = sd_noise, 
    n_post = n_post, constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s,
    optimum_true = optimum_true, non_optima = non_optima
  )
  stopCluster(cl)
  res %>%
    map_df(~ tibble(
    opt_in = .x$opt_in,
    area = .x$area,
    non_opt_in_1 = .x$non_opt_in[1],
    non_opt_in_2 = .x$non_opt_in[2],
    non_opt_in_3 = .x$non_opt_in[3],
    non_opt_in_4 = .x$non_opt_in[4],
    non_opt_in_5 = .x$non_opt_in[5],
    non_opt_in_6 = .x$non_opt_in[6],
    non_opt_in_7 = .x$non_opt_in[7],
    non_opt_in_8 = .x$non_opt_in[8],
    non_opt_in_9 = .x$non_opt_in[9],
    non_opt_in_10 = .x$non_opt_in[10],
  )) %>%
  mutate(area_sd = sd(area)) %>%
  select(opt_in, area, area_sd, 3:12) %>%
  map(mean) %>%
  set_names(
    c(
      "opt_coverage", "CR_area_mean", "CR_area_sd",
      unlist(lapply(X = 1:10, FUN = function(i) paste("non_opt_coverage_", i, sep = "")))
    )
  ) %>%
  unlist() %>%
  as.matrix(nrow = 13)
}
```

```{r eval=FALSE, include=FALSE}
rm(
  list = c(
    "beta_hat", "betas_post", "design", "f", "optimum_mean", "res", "y",
    "n_post", "n_rep", "sd_noise"
  )
)
```

```{r eval=FALSE, include=FALSE}
# only for development
coverage_analysis <- cover_multiple_time(
  sd_noise = 2, n_rep = 10, n_post = 200, n_cov = 10,
  design_no_rep = design_no_rep, beta_true = beta_true,
  constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s,
  optimum_true = optimum_true, non_optima = non_optima
)
```

```{r include=FALSE}
# Parameters for the coverage analysis
param_coverage_analysis <- tibble(
  sd_noise =  c(rep(2, 3), rep(5, 3), rep(10, 3)),
  n_rep = rep(c(100, 200, 500), 3)
)
```

```{r eval=FALSE, include=FALSE}
param_coverage_analysis
```

```{r eval=FALSE, include=FALSE}
# Coverage analyses with different parameters
coverage_analysis <- purrr::partial(
  cover_multiple_time,
  n_post = 1e3, n_cov = 1e3,
  design_no_rep = design_no_rep, beta_true = beta_true,
  constr_lb = constr_lb, constr_ub = constr_ub, x0s = x0s,
  optimum_true = optimum_true, non_optima = non_optima
)
run_time <- system.time(
  coverage_analyses <- param_coverage_analysis %>%
    pmap(~ coverage_analysis(sd_noise = ..1, n_rep = ..2)) %>%
    unlist() %>%
    matrix(nrow = 9, byrow = TRUE) %>%
    as_tibble() %>%
    set_names(
      c(
        "coverage", "area_mean", "area_sd",
        unlist(lapply(X = 1:10, FUN = function(i) paste("bias_", i, sep = "")))
      )
    ) %>%
    cbind(param_coverage_analysis) %>%
    select(14:15, 1:3, 4:13)
)
# save(coverage_analyses, file = "coverage_analyses_1e3_1e3.RData")
# save(run_time, file = "run_time_1e3_1e3.RData")
```

```{r include=FALSE}
load("~/Dropbox/P/PennState/ESAMLab/OptimaRegion-Package/OptimaRegion/vignettes/run_time_1e3_1e3.RData")
load("~/Dropbox/P/PennState/ESAMLab/OptimaRegion-Package/OptimaRegion/vignettes/coverage_analyses_1e3_1e3.RData")
```

```{r}
run_time / 3600
```

```{r}
coverage_analyses[, 1:5]
```

```{r}
coverage_analyses[, -(1:5)]
```

## 2. Credible Regions on Gussian Process Models

```{r, include = FALSE}
rm(list = rm(list=setdiff(ls(), "plot.bayescrquad")))
```

### 2.1 One-Dimensional Case

#### 2.1.0 Simulate Experimental Data

```{r}
n <- 15
sd_noise <- 0.05
flex_1 <- function(x) dnorm(x, mean = 3.5, sd = 0.7) + dnorm(x, mean = 1, sd = 1)
optimum_true <- 3.5
non_optima <- 1:5
design <- seq(0, 5, length.out = n)
response <- map_dbl(design, flex_1)
set.seed(123)
y <- response + rnorm(n = length(response), mean = 0, sd = sd_noise)
```

```{r include=FALSE}
plot_obs <- 
  ggplot(
    data = tibble(design = design, y = y),
    aes(x = design, y = y)
  ) + 
  geom_point() + 
  stat_function(fun = flex_1) + 
  geom_vline(xintercept = 3.5) + 
  xlab("x") + 
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "none") 
```

```{r}
plot_obs
```


#### 2.1.1 Draw Posterior Samples $\{\theta^{[t]}\}$
```{r}
draw_post_gp <- function(design, y, process_mean_lb, process_mean_ub,
                         length_scale_lb, length_scale_ub,
                         fun_var_lb, fun_var_ub, noise_var_lb, noise_var_ub,
                         chain_length) {
  # define the bayesian model
  gp_model <- "model{
    # likelihood
    y ~ dmnorm(mu, inverse(Sigma))
      for(i in 1:length(y)) {
        mu[i] <- process_mean
      }
      for(i in 1:(length(y) - 1)) {
        for(j in (i + 1):length(y)) {
          Sigma[i, j] <- fun_var * exp(- d[i, j] / length_scale)
          Sigma[j, i] <- Sigma[i, j]
        }
      }
      for(i in 1:length(y)) {
        Sigma[i, i] <- fun_var + noise_var
      }
    # prior
    process_mean ~ dunif(process_mean_lb, process_mean_ub)
    length_scale ~ dunif(length_scale_lb, length_scale_ub)
    fun_var ~ dunif(fun_var_lb, fun_var_ub)
    noise_var ~ dunif(noise_var_lb, noise_var_ub)
  }"
  # compile the bayesian model
  gp_jags <- jags.model(
    textConnection(gp_model),
    data = list(
      y = y, d = fields::rdist(design),
      process_mean_lb = process_mean_lb, process_mean_ub = process_mean_ub,
      length_scale_lb = length_scale_lb, length_scale_ub = length_scale_ub,
      fun_var_lb = fun_var_lb, fun_var_ub = fun_var_ub,
      noise_var_lb = noise_var_lb, noise_var_ub = noise_var_ub
    ),
    inits = list(.RNG.name = "base::Wichmann-Hill", .RNG.seed = 100),
    quiet = TRUE
  )
  # simulate posterior parameters
  gp_sim <- coda.samples(
    model = gp_jags,
    variable.names = c("process_mean", "length_scale", "fun_var", "noise_var"),
    n.iter = chain_length
  )
  # extract useful 
  gp_chain <- data.frame(gp_sim[[1]]) %>%
    dplyr::select(process_mean, length_scale, fun_var, noise_var)
  # return
  return(gp_chain)
}
```

```{r}
thetas <- draw_post_gp(
  design = design, y = y, process_mean_lb = -3, process_mean_ub = 3,
  length_scale_lb = 0, length_scale_ub = 10,
  fun_var_lb = 0, fun_var_ub = 2, noise_var_lb = 0, noise_var_ub = 1,
  chain_length = 1000
)
```

#### 2.1.2 Compute Posterior Mean Optimal Point $x^{*\overline{[t]} \, \overline{(s)}}$

```{r}
theta_mean <- purrr::map(thetas, mean)
```

```{r}
theta2mean_path <- function(design, y, process_mean, length_scale, x_grid) {
  kernel <- function(d) exp(-d / length_scale)
  R11 <- apply(X = fields::rdist(design), MARGIN = c(1, 2), FUN = kernel)
  R12 <- apply(X = fields::rdist(x1 = design, x2 = x_grid), MARGIN = c(1, 2), FUN = kernel)
  R22 <- apply(X = fields::rdist(x_grid), MARGIN = c(1, 2), FUN = kernel)
  rep(process_mean, nrow(x_grid)) + 
    crossprod(R12, solve(R11, y - rep(process_mean, length(y))))
}
```

```{r}
grid_size <- 200
x_grid <- seq(min(design), max(design), length.out = grid_size) %>% matrix(nrow = grid_size)
fun_hat <- theta2mean_path(
  design = design, y = y, 
  process_mean = theta_mean$process_mean, length_scale = theta_mean$length_scale,
  x_grid = x_grid
)
opt_hat <- x_grid[which.max(fun_hat)]
```

```{r include=FALSE}
plot_post_mean <- plot_obs + 
  geom_line(
    data = data.frame(x = x_grid, y = fun_hat),
    mapping = aes(x = x, y = y), 
    col = "blue"
  ) + 
  geom_vline(xintercept = opt_hat, col = "blue")
```

```{r}
plot_post_mean
```

#### 2.1.3 Use $x^{*\overline{[t]}\, \overline{(s)}}$ to Guide Sample Path Grid

```{r}
path_grid_1D <- function(design, n_new, xi, opt_hat, candidates) {
  path_grid <- design
  counter <- 0
  for (i in 1:n_new) {
    pt_score <- purrr::map_dbl(
      .x = candidates,
      .f = ~ min(fields::rdist(.x, path_grid)) - xi * fields::rdist(.x, opt_hat)
    )
    s_star <- candidates[which.max(pt_score)]
    candidates <- candidates[-which.max(pt_score)]
    path_grid <- c(path_grid, s_star)
  }
  path_grid %>% matrix(nrow = length(path_grid))
}
```

```{r}
path_grid <- path_grid_1D(
  design = design, n_new = 10, xi = 0.1, opt_hat = opt_hat, candidates = x_grid
)
```

```{r include=FALSE}
plot_path_grid <- plot_post_mean + 
  geom_point(
    data = tibble(x = path_grid, y = rep(0, length(path_grid))),
    aes(x, y), 
    size = 0.5, col = "blue"
  ) + 
  geom_point(
    data = tibble(x = design, y = rep(0, length(design))),
    aes(x,y),
    size = 0.5
  )
```

```{r}
plot_path_grid
```

#### 2.1.5 Thin $\{\theta^{[t]}\}$ to $\{\theta^{[\tau]}\}$

```{r}
thin_interval <- 5
thetas_thin <- slice(thetas, seq(0, nrow(thetas), by = thin_interval))
```

#### 2.1.6 Generate Sample Paths $\{y^{[\tau](s)}\}$ at the Grid

```{r}
theta2paths <- function(n_path, x_grid, design, y, process_mean, length_scale, fun_var) {
  kernel <- function(d) exp(-d / length_scale)
  R11 <- apply(X = fields::rdist(design), MARGIN = c(1, 2), FUN = kernel)
  R12 <- apply(X = fields::rdist(x1 = design, x2 = x_grid), MARGIN = c(1, 2), FUN = kernel)
  R22 <- apply(X = fields::rdist(x_grid), MARGIN = c(1, 2), FUN = kernel)
  mu <- rep(process_mean, nrow(x_grid))  +
    crossprod(R12, solve(R11, y - rep(process_mean, length(y))))
  Sigma <- fun_var * (R22 - crossprod(R12, solve(R11, R12)))
  MASS::mvrnorm(n = n_path, mu = mu, Sigma = Sigma) %>%
    matrix(nrow = n_path) %>%
    t() %>%
    as.data.frame() %>%
    set_names(map_chr(1:n_path, ~ paste("path_", .x, sep = "")))
}
```

```{r}
thetas2paths <- function(thetas, n_path_per_theta, x_grid, design, y)
  lapply(
    X = 1:nrow(thetas),
    FUN = function(i) theta2paths(
        n_path = n_path_per_theta, x_grid = x_grid, design = design, y = y,
        process_mean = thetas$process_mean[i],
        length_scale = thetas$length_scale[i],
        fun_var = thetas$fun_var[i]
      )
  )
```

```{r}
thetas2paths_par <- function(thetas, n_path_per_theta, x_grid, design, y) {
  cl <- makeCluster(detectCores(logical = FALSE) - 1)
  clusterEvalQ(cl, {
    library(tidyverse)
  })
  clusterExport(cl, "theta2paths")
  res <- lapply(
    X = 1:nrow(thetas),
    FUN = function(i) theta2paths(
        n_path = n_path_per_theta, x_grid = x_grid, design = design, y = y,
        process_mean = thetas$process_mean[i],
        length_scale = thetas$length_scale[i],
        fun_var = thetas$fun_var[i]
      )
  )
  stopCluster(cl)
  res
}
```


```{r}
paths <- thetas2paths (
  thetas = thetas_thin, n_path_per_theta = 10, x_grid = path_grid, design = design, y = y
)
```

```{r, include=FALSE}
plot_data_paths <- paths %>%
  purrr::imap(
    .f = ~ `names<-`(.x, paste0("theta_", .y, "_", names(.x)))
  ) %>%
  purrr::imap(
    .f = ~ mutate(.x, theta_id = paste0("theta_", .y))
  ) %>%
  purrr::map(
    .f = ~ mutate(.x, path_grid = path_grid %>% as.numeric())
  ) %>%
  purrr::map(
    .f = ~ pivot_longer(
      data = .x,
      col = c(-"theta_id", -"path_grid"),
      names_to = "path_id",
      values_to = "path_values"
    )
  ) %>%
  purrr::reduce(rbind) %>%
  mutate(theta_id = factor(theta_id), path_id = factor(path_id))
```

```{r include=FALSE}
plot_paths <- plot_path_grid + 
  geom_line(
    data = plot_data_paths,
    aes(x = path_grid, y = path_values, group = path_id, col = theta_id),
    alpha = 0.5
  ) + 
  geom_point(
    data = plot_data_paths,
    aes(x = path_grid, y = path_values, group = path_id, col = theta_id),
    size = 0.7,
    alpha = 0.5
  ) + 
  geom_line(
    data = data.frame(x = x_grid, y = fun_hat),
    mapping = aes(x = x, y = y), 
    col = "blue"
  ) 
```

#### 2.1.7 Map $\{y^{[\tau](s)}\}$ to $\{x^{*[\tau](s)}\}$

```{r}
paths2optima <- function(paths, path_grid) {
  purrr::map(
    .x = paths,
    .f = ~ path_grid[apply(.x, 2, which.max)]
  )
}
```

```{r}
optima <- paths2optima(paths = paths, path_grid = path_grid)
```


```{r include=FALSE}
plot_data_opt <- optima %>%
  purrr::imap(
    ~ tibble(opt = .x, theta_id = factor(.y))
  ) %>%
  purrr::reduce(rbind)
```


```{r include=FALSE}
plot_optima <- plot_paths + 
  geom_vline(
    data = plot_data_opt,
    aes(xintercept = opt),
    alpha = 0.5, col = "gray"
  )
```

```{r}
plot_optima
```


#### 2.1.3 Main Function


```{r}
BayesOptRegionGP1 <- function(design, y,
                              chain_length, thin_interval, n_path_per_theta,
                              n_new, xi,
                              process_mean_lb, process_mean_ub,
                              length_scale_lb, length_scale_ub,
                              fun_var_lb, fun_var_ub, noise_var_lb, noise_var_ub,
                              parallel = TRUE) {
  # draw posterior samples
  thetas <- draw_post_gp(
    design = design, y = y,
    process_mean_lb = process_mean_lb, process_mean_ub = process_mean_ub,
    length_scale_lb = length_scale_lb, length_scale_ub = length_scale_ub,
    fun_var_lb = fun_var_lb, fun_var_ub = fun_var_ub,
    noise_var_lb = noise_var_lb, noise_var_ub = noise_var_ub,
    chain_length = chain_length
  )
  # use posterior mean kriging optimum to guide sample path grid
  theta_mean <- purrr::map(thetas, mean)
  base_grid_size <- 200
  base_grid <- seq(min(design), max(design), length.out = base_grid_size) %>%
    matrix(nrow = base_grid_size)
  fun_hat <- theta2mean_path(
    design = design, y = y,
    process_mean = theta_mean$process_mean, length_scale = theta_mean$length_scale,
    x_grid = base_grid
  )
  opt_hat <- base_grid[which.max(fun_hat)]
  path_grid <- path_grid_1D(
    design = design, n_new = n_new, xi = xi, opt_hat = opt_hat, candidates = base_grid
  )
  # thin the posterior draws
  thetas_thin <- dplyr::slice(thetas, seq(0, nrow(thetas), by = thin_interval))
  # map thinned posterior draws to sample paths
  if (parallel) {
    paths <- thetas2paths_par(
      thetas = thetas_thin, n_path_per_theta = n_path_per_theta,
      x_grid = path_grid, design = design, y = y
    )
  } else {
    paths <- thetas2paths(
      thetas = thetas_thin, n_path_per_theta = n_path_per_theta,
      x_grid = path_grid, design = design, y = y
    )
  }
  # map sample paths to optima
  optima <- paths2optima(paths = paths, path_grid = path_grid)
  # return
  ## for development
  # list(
  #   thetas = thetas, theta_mean = theta_mean, opt_hat = opt_hat, path_grid = path_grid,
  #   thetas_thin = thetas_thin, paths = paths, optima = optima
  # )
  ## for publication
  list(
    thetas = structure(thetas, class = "mcmcdraw"),
    thetas_thin = structure(thetas_thin, class = "mcmcdraw"),
    optima = structure(unlist(optima), class = "bayesoptima1D")
  )
}
```

```{r include=FALSE}
plot.mcmcdraw <- function(thetas) {
  attr(thetas, "class") <- "data.frame"
  traces <- purrr::imap(
    thetas,
    ~ ggplot(thetas, aes(x = 1:length(.x), y = .x)) +
      geom_line() +
      geom_smooth(method = "lm", col = "red") +
      xlab("Iterations") +
      ylab("") +
      ggtitle(paste("trace of posterior", .y)) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5)
      )
  )
  densities <- purrr::imap(
    thetas,
    ~ ggplot(thetas, aes(x = .x)) +
      geom_density() +
      xlab("Iterations") +
      ylab("") +
      ggtitle(paste("density of posterior", .y)) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5)
      )
  )
  grid.arrange(
    grobs = c(traces, densities),
    layout_matrix = matrix(1:8, nrow = 4)
  )
}
```

```{r include=FALSE}
summary.mcmcdraw <- function(thetas) {
  attr(thetas, "class") <- "data.frame"
  purrr::map(thetas, ~ quantile(x = .x, probs = c(0.025, 0.25, 0.5, 0.75, 0.975))) %>%
    unlist() %>%
    matrix(nrow = 4, byrow = TRUE) %>%
    `rownames<-`(names(thetas)) %>%
    `colnames<-`(c("2.5%", "25%", "50%", "75%", "97.5%"))
}
```

```{r include=FALSE}
plot.bayesoptima1D <- function(optima){
  optima <- unlist(optima)
  optima_quantile <- quantile(optima, c(0.025, 0.975))
  optima <- optima[optima >= optima_quantile[1] & optima <= optima_quantile[2]]
  ggplot(mapping = aes(x = optima )) + 
    geom_histogram(binwidth = 0.05, fill = "white", col = "black") + 
    xlab("posterior optima") + 
    ylab("frequency") + 
    ggtitle("Distribution of Mid-95% Posterior Optima") + 
    theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5)
      )
}
```

```{r include=FALSE}
summary.bayesoptima1D <- function(optima) {
  quantile_optima <- quantile(unlist(optima), c(0.025, 0.975))
  paste0(
    "95% credible interval of the optimal point: [",
    quantile_optima[1] %>% round(2),
    ", ",
    quantile_optima[2] %>% round(2),
    "]"
  )
}
```


```{r}
c(thetas, thetas_thin, optima) %<-% BayesOptRegionGP1(
  design = design, y = y,
  chain_length = 10000, thin_interval = 25, n_path_per_theta = 100,
  n_new = 100, xi = 0.1,
  process_mean_lb = -3, process_mean_ub = 3,
  length_scale_lb = 0, length_scale_ub = 10,
  fun_var_lb = 0, fun_var_ub = 2, noise_var_lb = 0, noise_var_ub = 1
)
```


```{r fig.height=10, fig.width=7}
plot(thetas)
```

```{r}
summary(thetas)
```

```{r fig.height=10, fig.width=7}
plot(thetas_thin)
```

```{r}
summary(thetas_thin)
```

```{r}
plot(optima)
```
```{r}
summary(optima)
```

#### 2.1.5 Coverage Analyses

```{r eval=FALSE, include=FALSE}
BayesOptRegionGP1_analysis <- purrr::partial(
  BayesOptRegionGP1, 
  chain_length = 10000, thin_interval = 25, n_path_per_theta = 100,
  n_new = 100,
  process_mean_lb = -3, process_mean_ub = 3,
  length_scale_lb = 0, length_scale_ub = 10,
  fun_var_lb = 0, fun_var_ub = 2, noise_var_lb = 0, noise_var_ub = 1,
  parallel = FALSE
)
```

```{r eval=FALSE, include=FALSE}
noise2CR <- function(i, design, response, sd_noise, xi, optimum_true, non_optima) {
  paste0(i, " th CR with sd_noise = ", sd_noise, " and n = ", length(design)) %>%
    print()
  c(thetas, thetas_thin, optima) %<-% BayesOptRegionGP1_analysis(
    design = design, y = response + rnorm(n = length(response), mean = 0, sd = sd_noise),
    xi = xi
  )
  optima_quantile <- quantile(unlist(optima), c(0.025, 0.975))
  opt_in <- ifelse(
    optimum_true >= optima_quantile[1] && optimum_true <= optima_quantile[2],
    TRUE, FALSE
  )
  area <- optima_quantile[2] - optima_quantile[1]
  non_opt_in <- purrr::map_lgl(
    .x = non_optima,
    .f = ~ ifelse(
      .x >= optima_quantile[1] && .x <= optima_quantile[2], TRUE, FALSE
    )
  )
  list(opt_in = opt_in, area = area, non_opt_in = non_opt_in, CR = optima_quantile)
}
```

```{r eval=FALSE, include=FALSE}
noise2CR(
  i = 1, design = design, response = response, sd_noise = 0.05, xi = 0.1, 
  optimum_true = optimum_true, non_optima = non_optima
)
```

```{r eval=FALSE, include=FALSE}
noises2CRs <- function(sd_noise, n, xi, optimum_true, non_optima, n_cov) {
  design <- seq(0, 5, length.out = n)
  response <- map_dbl(design, flex_1)
  cl <- makeCluster(detectCores(logical = FALSE) - 1, outfile = "")
  clusterEvalQ(cl, {
    library(tidyverse)
    library(keras)
    library(rjags)
  })
  clusterExport(
    cl, c(
      "noise2CR",
      "BayesOptRegionGP1_analysis", "BayesOptRegionGP1",
      "draw_post_gp", "theta2mean_path", "path_grid_1D", 
      "theta2paths", "thetas2paths", "thetas2paths_par", "paths2optima"
    )
  )
  res <- clusterApply(
    cl = cl, x = 1:n_cov, fun = noise2CR,
    design = design, response = response, sd_noise = sd_noise, xi = xi,
    optimum_true = optimum_true, non_optima = non_optima
  )
  stopCluster(cl)
  res %>%
    purrr::map_df(
      ~ tibble(
        opt_in = .x$opt_in,
        area = .x$area,
        non_opt_in_1 = .x$non_opt_in[1],
        non_opt_in_2 = .x$non_opt_in[2],
        non_opt_in_3 = .x$non_opt_in[3],
        non_opt_in_4 = .x$non_opt_in[4],
        non_opt_in_5 = .x$non_opt_in[5],
      )
    ) %>%
    mutate(area_sd = sd(area)) %>%
    dplyr::select(opt_in, area, area_sd, 3:7) %>%
    purrr::map(mean) %>%
    set_names(
      c(
        "coverage", "area_mean", "area_sd",
        unlist(lapply(X = 1:5, FUN = function(i) paste0("bias_", i)))
      )
    ) %>%
    unlist()
}
```

```{r eval=FALSE, include=FALSE}
res <- noises2CRs(
  sd_noise = 0.05, n = 25, xi = 0.1,
  optimum_true = optimum_true, non_optima = non_optima, n_cov = 5
)
```

```{r eval=FALSE, include=FALSE}
param_coverage_analysis <- tibble(
  sd_noise = 0.025,
  n = c(5, 10, 15, 20, 25),
  xi = 0.1
)
param_coverage_analysis
```

```{r eval=FALSE, include=FALSE}
run_time <- system.time(
  coverage_analyses <- param_coverage_analysis %>%
    purrr::pmap(
      ~ noises2CRs(
        sd_noise = ..1, n = ..2, xi = ..3, n_cov = 200,
        optimum_true = optimum_true, non_optima = non_optima
      )
    ) %>%
    unlist() %>%
    matrix(byrow = TRUE, nrow = nrow(param_coverage_analysis)) %>%
    `colnames<-`(
      c(
        "coverage", "area_mean", "area_sd",
        unlist(lapply(X = 1:5, FUN = function(i) paste0("bias_", i)))
      )
    ) %>%
    cbind(param_coverage_analysis) %>%
    dplyr::select(9:11, 1:3, 4:8)
)
# save(coverage_analyses, file = "coverage_gp_1D_1e4_200.RData")
# save(run_time, file = "time_gp_1D_1e4_200.RData")
```

```{r, include = FALSE}
load("~/Dropbox/P/PennState/ESAMLab/OptimaRegion-Package/OptimaRegion/vignettes/coverage_gp_1D_1e4_200.RData")
load("~/Dropbox/P/PennState/ESAMLab/OptimaRegion-Package/OptimaRegion/vignettes/time_gp_1D_1e4_200.RData")
```

```{r}
run_time / 3600
```

```{r}
coverage_analyses[, 1:6]
```
```{r}
coverage_analyses[, -(1:6)]
```


### 2.2 Two-Dimensional Case

```{r}
flex_2 <- function(x)
  ((x[1] - 2)^2 + (x[2] - 2)^2 - (x[1] - 2) + 2 * (x[1] - 2) * (x[2] - 2)) *
    exp(-(x[1] - 2)^2 - (x[2] - 2)^2)
optimum_true <- c(1.2542, 1.4634)
```

```{r}
n <- 25
sd_noise <- 0.5
```

```{r, include=FALSE}
outer2 <- function(x1_grid, x2_grid, fun) {
  row2values <- function(i) purrr::map_dbl(x2_grid, ~ fun(c(i, .x)))
  grid_values <- purrr::map(x1_grid, row2values) %>%
    unlist() %>%
    matrix(byrow = TRUE, nrow = grid_size) %>%
    `rownames<-`(x1_grid) %>%
    `colnames<-`(x2_grid) %>%
    as.data.frame() %>%
    rownames_to_column(var = "x1") %>%
    pivot_longer(cols = (-"x1"), names_to = "x2", values_to = "y") %>%
    mutate(x1 = as.numeric(x1), x2 = as.numeric(x2))
}
```


```{r, include=FALSE}
# prepare data
grid_size <- 100
x1_grid <- seq(0, 5, length.out = grid_size)
x2_grid <- x1_grid
grid_values <- outer2(x1_grid = x1_grid, x2_grid = x2_grid, fun = flex_2)
# plot contour
plot_RS <- ggplot(
  data = grid_values,
  aes(x = x1, y = x2)
) + 
  geom_raster(aes(fill = y)) + 
  geom_contour(aes(z = y), col = "black", size = 0.5) + 
  scale_fill_gradient(low = "yellow", high = "red") + 
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
```

```{r}
plot_RS
```

